---
title: "assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
```

```{r}
stocks <- read.csv("stocks.csv")
nrow(stocks)
head(stocks)
#stocks <- na.omit(stocks)
#nrow(stocks)
```

147 variables with 102 having the missing value

```{r}
summary(stocks)
```

- Trailing P/E is calculated by dividing the current market value, or share price, by the earnings per share over the previous 12 months.
- The forward P/E ratio estimates a company's likely earnings per share for the next 12 months.
- The PEG ratio enhances the P/E ratio by adding in expected earnings growth into the calculation. The PEG ratio is considered to be an indicator of a stock's true value, and similar to the P/E ratio, a *lower PEG may indicate that a stock is undervalued*.
- The P/S ratio is a key analysis and valuation tool that shows how much investors are willing to pay per dollar of sales for a stock. The P/S ratio is typically calculated by dividing the stock price by the underlying company's sales per share.A low ratio could imply the stock is undervalued while a ratio that is higher-than-average could indicate that the stock is overvalued.
- The P/B ratio measures the market's valuation of a company relative to its book value.The market value of equity is typically higher than the book value of a company.P/B ratio is used by value investors to identify potential investments. P/B ratios under 1 are typically considered solid investments.
- The enterprise value-to-revenue (EV/R) multiple helps compares a company’s revenues to its enterprise value. The lower the better, in that, a lower EV/R multiple signals a company is undervalued.
- The enterprise value to earnings before interest, taxes, depreciation, and amortization ratio (EV/EBITDA) compares the value of a company—debt included—to the company’s cash earnings less non-cash expenses. The EV/EBITDA metric is a popular valuation tool that helps investors compare companies in order to make an investment decision. EV calculates a company's total value or assessed worth, while EBITDA measures a company's overall financial performance and profitability. Typically, when evaluating a company, *an EV/EBITDA value below 10 is seen as healthy*. It's best to use the EV/EBITDA metric when comparing companies within the same industry or sector.
```{r}
stocks %>% filter(Enterprise.value.EBITDA<10)
```

```{r}
stocks %>% filter(Industry == "Technology")
```

