---
title: "assignment"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
library(dplyr)
library(ggplot2)
```

```{r data}
stocks <- read.csv("stocks.csv")
nrow(stocks)
head(stocks)
stocks <- na.omit(stocks)%>%
  rename(intra_day=Market.cap..intra.day.)%>%
  rename(ent_value=Enterprise.value)%>%
  rename(trail_pe=Trailing.P.E)%>%
  rename(for_pe=Forward.P.E)%>%
  rename(peg=PEG.ratio..5.yr.expected.)%>%
  rename(ttm=Price.sales..ttm.)%>%
  rename(mrq=Price.book..mrq.)%>%
  rename(rev=Enterprise.value.revenue)%>%
  rename(ebitda=Enterprise.value.EBITDA)
#stocks <- na.omit(stocks)
#nrow(stocks)
```

147 variables with 102 having the missing value

```{r}
summary(stocks)
```

## Description of the variables related to the value of stocks:
- Market capitalization refers to how much a company is worth as determined by the stock market. It is defined as the total market value of all outstanding shares. To calculate a company's market cap, multiply the number of outstanding shares by the current market value of one share. Companies are typically divided according to market capitalization: large-cap (\$10 billion or more), mid-cap (\$2 billion to \$10 billion), and small-cap (\$300 million to \$2 billion). Enterprise value includes in its calculation the market capitalization of a company but also short-term and long-term debt as well as any cash on the company's balance sheet. Enterprise value is used as the basis for many financial ratios that measure the performance of a company.
- Enterprise value (EV) is a measure of a company's total value, often used as a more comprehensive alternative to equity market capitalization.
- Trailing P/E is calculated by dividing the current market value, or share price, by the earnings per share over the previous 12 months.
- The forward P/E ratio estimates a company's likely earnings per share for the next 12 months.
- The PEG ratio enhances the P/E ratio by adding in expected earnings growth into the calculation. The PEG ratio is considered to be an indicator of a stock's true value, and similar to the P/E ratio, a *lower PEG may indicate that a stock is undervalued*.
- The P/S ratio is a key analysis and valuation tool that shows *how much investors are willing to pay per dollar of sales for a stock.* The P/S ratio is typically calculated by dividing the stock price by the underlying company's sales per share.A low ratio could imply the stock is undervalued while a ratio that is higher-than-average could indicate that the stock is overvalued.
- The P/B ratio measures the market's valuation of a company relative to its book value.*The market value of equity is typically higher than the book value of a company.* P/B ratio is used by value investors to identify potential investments. P/B ratios under 1 are typically considered solid investments.
- The enterprise value-to-revenue (EV/R) multiple helps compares a company’s revenues to its enterprise value. *The lower the better, in that, a lower EV/R multiple signals a company is undervalued.*
- The enterprise value to earnings before interest, taxes, depreciation, and amortization ratio (EV/EBITDA) compares the value of a company—debt included—to the company’s cash earnings less non-cash expenses. The EV/EBITDA metric is a popular valuation tool that helps investors compare companies in order to make an investment decision. EV calculates a company's total value or assessed worth, while EBITDA measures a company's overall financial performance and profitability. Typically, when evaluating a company, *an EV/EBITDA value below 10 is seen as healthy*. It's best to use the EV/EBITDA metric when comparing companies within the same industry or sector.

```{r}
stocks %>% 
  dplyr::filter(ebitda<10) %>% 
  ggplot(aes(ebitda, ebitda)) + 
  geom_boxplot() + 
  facet_wrap(~Industry)
```

## Value Analysis
```{r value}
issuer<-stocks%>%
  select(Symbol,intra_day,ent_value,trail_pe,for_pe,peg,ttm,mrq,rev,ebitda)

pca_value<-issuer%>%
  select(intra_day,ent_value,trail_pe,for_pe,peg,ttm,mrq,rev,ebitda)%>%
  prcomp(scale.=TRUE)
rownames(pca_value$x)<-pull(issuer,Symbol)
biplot(pca_value, expand=10,xlim=c(-0.5,0.6),ylim=c(-0.05,0.1))
```

```{r}
stocks %>% filter(Industry == "Technology")
```

## Risk 
```{r first_check}
d <- apply(cbind(stocks$Environmental.Risk.Score, stocks$Social.Risk.Score, stocks$Governance.Risk.Score), 1, sum)
all(stocks$Total.ESG.risk.score == d)
```

```{r risk data}
# checking if total esg risk score = environmrnt + social + government 
stocks_tesg <- stocks[stocks[,15] == d,]
d <- apply(cbind(stocks_tesg$Environmental.Risk.Score, stocks_tesg$Social.Risk.Score, stocks_tesg$Governance.Risk.Score), 1, sum)
all(stocks_tesg$Total.ESG.risk.score == d, na.rm = TRUE)
stocks_risk <- stocks_tesg %>% select(Symbol, Environmental.Risk.Score, Social.Risk.Score, Governance.Risk.Score)
```

```{r pca_risk}
pca_risk <- stocks_risk %>% select_if(is.numeric) %>% prcomp(scale. = TRUE)
rownames(pca_risk$x) <- pull(stocks_risk, Symbol)
biplot(pca_risk, xlim=c(-0.4,0.4), cex=0.7)
```



